Predicting sales of newly published books

### 2015-09-11 paper.tex
Revised English and practically removed Problem section refs #6 #11
updating terms in the .tex file

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICE
SUBJECT1
SUBJECT2
SUBJECT3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
MALLS SALES
DELEGATES SALES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED
REST OF DISTRIBUTED
TOTAL DISTRIBUTED FIRST YEAR
MALLS DISTRIBUTED FIRST YEAR
DELEGATES DISTRIBUTED FIRST YEAR
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS
MALLS DEVOLUTIONS
DELEGATES DEVOLUTIONS
REST OF DEVOLUTIONS
TOTAL DEVOLUTIONS FIRT YEAR
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES DEVOLUTIONS FIRST YEAR
REST OF DEVOLUTIONS FIRST YEAR
GIFTS
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
MALLS SELLING POINTS
DELEGATES SELLING POINTS
REST OF SELLING POINTS
TOTAL SELLING POINTS FIRST YEAR
MALLS SELLING POINTS FIRST YEAR
DELEGATES SELLING POINTS FIRST YEAR
REST OF SELLING POINTS FIRST YEAR
WEEKS FOR SALE
POSITIVE SALE MARKET
MEDIUM SALE MARKET
NEGATIVE SALE MARKET
\end{verbatim} \end{minipage}    \\

@@

In this prediction problem, several variables related to the own book affect 
the forecasts, such as author, price, subject or publisher.

However, there are other external variables that also affect the sales of 
a new book, such as those related to seasonality, trends or promotions, 
that classical prediction methods can not deal with.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on external data.

@@

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SELLING POINTS FIRST YEAR
REST OF SALES FIRST YEAR
NEGATIVE SALE MARKET
MALLS DISTRIBUTED FIRST YEAR
TOTAL DEVOLUTIONS
REPRINTS
MALL SALES FIRST YEAR
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
PRINT-RUN
NUMBER OF REPRINTS
MALLS DEVOLUTIONS
REST OF SELLING POINTS FIRST YEAR
REST OF SALES
DELEGATES SELLING POINTS
REST OF DEVOLUTIONS
DELEGATES SELLING POINTS FIRST YEAR
POSITIVE SALE MARKET
REST OF DISTRIBUTED FIRST YEAR
REST OF SELLING POINTS
TOTAL DEVOLUTIONS FIRT YEAR
DELEGATES DEVOLUTIONS
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED FIRST YEAR
MALLS SELLING POINTS
TOTAL SALES FIRST YEAR
MEDIUM SALE MARKET
WEEKS FOR SALE
DELEGATES DISTRIBUTED
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES SALES
REST OF DISTRIBUTED
DELEGATES DEVOLUTIONS FIRST YEAR
TOTAL DISTRIBUTED
REST OF DEVOLUTIONS FIRST YEAR
RETAIL PRICE
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL DEVOLUTIONS
REPRINTS
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
WEEKS FOR SALE
TOTAL DISTRIBUTED
RETAIL PRICE
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

>>>>

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICER
SUBJECT1
SUBJECT2
SUBJECT3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
DEPARTMENT STORES SALES
SALES THROUGH DELEGATES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
DISTRIBUTED THROUGH DEPARTMENT STORES
DISTRIBUTED THROUGH DELEGATES
DISTRIBUTED - REST
TOTAL DISTRIBUTED FIRST YEAR
DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
DISTRIBUTED THROUGH DELEGATES FIRST YEAR
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL RETURNS
RETURNS - DEPARTMENT STORES
DELEGATES RETURNS
REST OF RETURNS
TOTAL RETURNS FIRT YEAR
RETURNS -  DEPARTMENT STORES  FIRST YEAR
DELEGATES RETURNS FIRST YEAR
REST OF RETURNS FIRST YEAR
GIFTS
UNITS DISTRIBUTED AS NOVELTY
TOTAL POINTS OF SALE
POINTS OF SALE - DEPARTMENT STORES
DELEGATES POINTS OF SALE
REST OF POINTS OF SALE
TOTAL POINTS OF SALE FIRST YEAR
DEPARTMENT STORES POINTS OF SALE FIRST YEAR
DELEGATES POINTS OF SALE FIRST YEAR
REST OF POINTS OF SALE FIRST YEAR
WEEKS FOR SALE
POSITIVE SALES ENVIRONMENT
MEDIUM SALES ENVIRONMENT
NEGATIVE SALES ENVIRONMENT
\end{verbatim} \end{minipage}    \\

@@

In this prediction problem, several variables related to the own book affect 
the forecasts, such as author, price, subject or publisher. %This has
                                %to be grounded by the experiment and
                                %graphs.

However, there are other external variables that also affect the sales of 
a new book, such as those related to seasonality, trends or promotions, 
that classical prediction methods can not deal with.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. %so what?

@@

\begin{minipage}{2.3in} \begin{verbatim}
DEPARTMENT STORES POINTS OF SALE FIRST YEAR
REST OF SALES FIRST YEAR
NEGATIVE SALES ENVIRONMENT
DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
TOTAL RETURNS
REPRINTS
MALL SALES FIRST YEAR
TOTAL POINTS OF SALE FIRST YEAR
UNITS DISTRIBUTED AS NOVELTY
PRINT-RUN
NUMBER OF REPRINTS
RETURNS - DEPARTMENT STORES
REST OF POINTS OF SALE FIRST YEAR
REST OF SALES
DELEGATES POINTS OF SALE
REST OF RETURNS
DELEGATES POINTS OF SALE FIRST YEAR
POSITIVE SALES ENVIRONMENT
REST OF DISTRIBUTED FIRST YEAR
REST OF POINTS OF SALE
TOTAL RETURNS FIRT YEAR
DELEGATES RETURNS
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
DEPARTMENT STORES SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL POINTS OF SALE
DISTRIBUTED THROUGH DEPARTMENT STORES
DISTRIBUTED THROUGH DELEGATES FIRST YEAR
POINTS OF SALE - DEPARTMENT STORES
TOTAL SALES FIRST YEAR
MEDIUM SALES ENVIRONMENT
WEEKS FOR SALE
DISTRIBUTED THROUGH DELEGATES
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
RETURNS -  DEPARTMENT STORES  FIRST YEAR
SALES THROUGH DELEGATES
DISTRIBUTED - REST
DELEGATES RETURNS FIRST YEAR
TOTAL DISTRIBUTED
REST OF RETURNS FIRST YEAR
RETAIL PRICER
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL RETURNS
REPRINTS
TOTAL POINTS OF SALE FIRST YEAR
UNITS DISTRIBUTED AS NOVELTY
NUMBER OF REPRINTS
TOTAL RETURNS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL POINTS OF SALE
WEEKS FOR SALE
TOTAL DISTRIBUTED
RETAIL PRICER
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\
